Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-03 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
upd table and bib

% ---------------------------
% CONCRETE EXAMPLE OF MAPPING
% ---------------------------
Let us show one concrete example of how this mapping is done.
%
In Ref.~\cite{Wagle:2021tam} the QNMs of slow-rotating BHs in dCS gravity were calculated
and it was found that the axial gravitational modes have their damping time increased as we
increase the Chern-Simons coupling $\ell_{\rm CS}$ at fixed spin $\chi$ of the BH.
%
Having selected this branch of QNMs we can proceed to determine $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
%
Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
%
\begin{equation}
    M \omega^{\rm CS}_{220} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
    \label{eq:omega_dsc_eg}
\end{equation}
%
and similarly for the imaginary part ${\rm Im}(\sigma_{220}) = \omega^{\rm CS}_{220} = 1 / \tau^{\rm CS}_{220}$.
%
Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [thus $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
and $c_{i}$ are fitting coefficients.
%
In the context of a binary BH merger, $M$ is interpreted as the remnant mass $\Mf$.

@@

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
EdGB      & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
cEFTofGR  & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
% qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
only parity-even corrections and the second entries by considering
only parity-odd corrections.
%
In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
with the length scale $\ell$.
%
}
\label{tab:ref_theories_qnms}
\end{table*}

>>>>

% ---------------------------
% CONCRETE EXAMPLE OF MAPPING
% ---------------------------
Let us show one concrete example of how this mapping is done.
%
In Ref.~\cite{Wagle:2021tam} the QNMs of slow-rotating BHs in dCS gravity were calculated
and it was found that the axial gravitational modes have their damping time increased as we
increase the Chern-Simons coupling $\ell_{\rm CS}$ at fixed spin $\chi$ of the BH.
%
Having selected this branch of QNMs we can proceed to determine $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
%
Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
%
\begin{equation}
    M \omega^{\rm CS}_{220} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
    \label{eq:omega_dsc_eg}
\end{equation}
%
and similarly for the imaginary part ${\rm Im}(\sigma_{220}) =  - 1 / \tau^{\rm CS}_{220}$.
%
Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [thus $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
and $c_{i}$ are fitting coefficients.
%
In the context of a binary BH merger, $M$ is interpreted as the remnant mass $\Mf$.

@@

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
EdGB      & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
cEFT  & 4 & -0.5812  & 1.3234 & \dots & \dots & \cite{Cano:2021myl} & \dots  & \dots \\
qEFT  & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl} & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
% In the entries for cEFTofGR, the first entries in the $\delta
% \omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
% only parity-even corrections and the second entries by considering
% only parity-odd corrections.
%
In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
with the length scale $\ell$.
%
}
\label{tab:ref_theories_qnms}
\end{table*}
